---
title: "Homework 5"
author: "Mingee Choi"
date: 11/16/2022
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(broom)
library(patchwork)

set.seed(10)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 2

###Description of raw data:
```{r}
homicide_data=
  read_csv("./data/homicide-data.csv")%>%
  janitor::clean_names()%>%
  mutate(reported_date = lubridate::ymd(reported_date))%>%
  drop_na(reported_date)
```
The `homicide_data` has `r nrow(homicide_data)` observations and `r ncol(homicide_data)` variables and tells us about homicides in 50 large U.S. cities a given year from years `r range(homicide_data$reported_date)[1]` to `r range(homicide_data$reported_date)[2]`. The variables include victim's first name, victim's second name, victim's age, victim's sex, city, state, latitude, longitude, and disposition.

###Create variable and summarize 
Create city_state variable and summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which disposition is "closed without arrest" or "open/no arrest")
```{r}
homicide_df=
homicide_data%>%
  mutate(city_state= str_c(city, state, sep=",")
  )%>%
  select(uid,city_state,everything())%>%
  group_by(city_state)%>%
  summarize(total_homicides = n(),  unsolved_homicides = sum(disposition%in%c("Closed without arrest", "Open/No arrest")))%>%
  arrange(desc(total_homicides))
```

###Use prop.test for city of Baltimore, MD

```{r}
baltimore_test=
  homicide_df%>%
  filter(city_state == "Baltimore,MD")%>%
  mutate(prop_test = map2(unsolved_homicides, total_homicides, ~prop.test(.x, .y)%>%
  broom::tidy()))%>%
  unnest()

save(baltimore_test, file="baltimore_test.RData")

  baltimore_test%>%
  select(city_state, estimate, "CI_lower" = conf.low, "CI_upper" = conf.high)
```

###Prop.test for each cities
prop.test for each cities in dataset and extract both the proportion of unsolved homicides and the confidence interval for each
```{r}
prop_test=
  homicide_df%>%
  mutate(prop_test = map2(unsolved_homicides, total_homicides, ~prop.test(.x, .y)%>%
  broom::tidy()))%>%
  unnest()

prop_test%>%
 select(city_state, estimate, "CI_lower" = conf.low, "CI_upper" = conf.high)
```

###Plot of estimates and CIs for each city
```{r}
prop_test%>%
  arrange(desc(estimate))%>%
 ggplot(aes(group = city_state, y = reorder(city_state, estimate))) + 
 geom_point(aes(x = estimate)) +
 geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) +
 labs(y = "City,State", x = "Estimate and 95% CI",title = "Unsolved Homicides")
```

# Problem 3






