---
title: "Homework 5"
author: "Mingee Choi"
date: 11/16/2022
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 2

Description of raw data:
```{r}
homicide_data=
  read_csv("./data/homicide-data.csv")%>%
  janitor::clean_names()%>%
  mutate(reported_date = lubridate::ymd(reported_date))%>%
  drop_na(reported_date)
```
The `homicide_data` has `r nrow(homicide_data)` observations and `r ncol(homicide_data)` variables and tells us about homicides in 50 large U.S. cities a given year from years `r range(homicide_data$reported_date)[1]` to `r range(homicide_data$reported_date)[2]`. The variables include victim's first name, victim's second name, victim's age, victim's sex, city, state, latitude, longitude, and disposition.

# Problem 3
